Embodied Neuromorphic Benchmarks

### 2015-08-10 paper/paper.tex
Added refs

First, we note that the problem faced here is remarkably similar to a problem
faced by the evolutionary robotics community.  In evolutionary robotics, the
goal is to use genetic algorithms to \emph{evolve} systems that can control
robots to perform various tasks.  These tasks can be as simple as navigation
and obstacle avoidance, but have also included complex eight-legged walking,
object identification, and visual tracking [refs???].

@@

It is also worth noting that a minimal simulation \emph{only has to be a
good simulation for successful behaviour}.  That is, ``if we are evolving 
corridor following behaviour, the dynamics of the simulation might
differ wildly from those of reality if the controller hits a wall or
goes round in circles, but this does
not matter, since the controllers we are interested in transferring
across the reality gap will neither
hit walls nor go round in circles.''  If the controller is poor, we do not 
need the simulation to be at all accurate in exactly \emph{how} that poor
behaviour is manifest.  We do not need an exact detailed physics model of
the collision between a robot and a wall, or a detailed model of what happens
to a robot arm when it starts oscillating wildly due to a poor control signal.
All we need is for the simulation to be just good enough to indicate that
things have gone wrong, and thus give a low score to that controller.

@@

All of that said, we also need real physical embodiment as part of any
benchmark of this kind.  While we claim that reliable minimal simulations
are relatively easy to create, they are not a widely-used technique, and the
real proof of behaviour is always in the real world.  For this reason, we
also argue that every benchmark based on a minimal simulation should also
have an easy-to-construct physical analog.  However, this physical version
is not to be used as the primary benchmark.  Rather, this is meant as a
double-check that the system does actually behave as expected.  The worry
is always that if researchers focus on the simulated system when benchmarking
their hardware, they may inadvertantly end up with hardware that only performs
well in simulation.

@@

The simplest controller for such a situation is a P (proportional) controller,
where $u=K_p(q_d - q)$.  This is often supplemented with a derivative term,
which helps to slow the system down as it approaches the desired position,
thus avoiding overshooting and oscillation ($u=K_p(q_d - q) + K_d(\dot{q_d} - \dot{q})$),
leading to the standard PD controller.  Both $K_p$ and $K_d$ are constants that can be
tuned to particular situations.

@@

The standard solution to this problem is to add an integral term ($K_i \int{q_d-q dt}$)
to the controller, making it a PID controller.  The idea here is that as the difference between where it is and
where we want it to be accumulates over time, the $K-i$ term gradually increases
how much extra force is being applied until it is large enough to counteract
the external force of gravity (or whatever other external forces are present).
However, this approach has great difficulty when $q_d$ changes, since the
external force due to gravity changes depending on the position of the arm $q$.
The controller ends up having to use the accumulated integral to ``relearn'' the
correct amount of extra force needed every time $q_d$ changes.

@@

Fortunately, there is an adaptive solution to this problem, and it is one that
fits well with neuromorphic hardware.  \cite{Slotine1987} shows that if you
express the influence of these other external forces as $\tau=Y(q) \omega$
(where $Y(q)$ is a fixed set of functions of $q$, such as $sin(q)$, and $\omega$
is a vector of weights, one for each function in $Y$), then you can learn
to compensate for these external forces by using the learning rule $\Delta \omega = \alpha Y(q) u$,
where $u$ is the basic PD control signal.

Importantly, as pointed out in [ref] and [ref], rather than making explicit
assumptions about the exact functions that should be in $Y(q)$, we can use
a neural network approach where each neuron is a different function of $q$.  
As long as there is enough hetereogenetity (i.e. as long as the neural activity
forms a basis space that spans the desired space of functions), then the
learning rule will continue to work.

>>>>

First, we note that the problem faced here is remarkably similar to a problem
faced by the evolutionary robotics community.  In evolutionary robotics, the
goal is to use genetic algorithms to \emph{evolve} systems that can control
robots to perform various tasks.  These tasks can be as simple as navigation
and obstacle avoidance, but have also included walking,
object identification, and visual tracking [refs???].

@@

It is also worth noting that a minimal simulation \emph{only has to be a
good simulation for successful behaviour}.  That is, ``if we are evolving 
corridor following behaviour, the dynamics of the simulation might
differ wildly from those of reality if the controller hits a wall or
goes round in circles, but this does
not matter, since the controllers we are interested in transferring
across the reality gap will neither
hit walls nor go round in circles.''  If the controller is poor, we do not 
need the simulation to be at all accurate in exactly \emph{how} that poor
behaviour is manifest.  We do not need an exact detailed physics model of
the collision between a robot and a wall, or a detailed model of what happens
to a robot arm when it starts oscillating wildly due to a poor control signal.
All we need is for the simulation to be just good enough to indicate that
things have gone wrong, and thus give a low score to that controller.  This
means that, for example, in a minimal simulation of an eight-legged walking robot,
it is not necessary to have a physics simulation that correctly models what
happens when two legs collide with each other.  Rather, if legs collide
with each other, that is an indication that the walking behaviour is very poor,
so as long as that result is indicated we can greatly simplify the simulation
by not including all the details necessary to deal with these sorts of physical
interactions.

@@

All of that said, we also need real physical embodiment as part of any
benchmark of this kind.  While we claim that reliable minimal simulations
are relatively easy to create, they are not a widely-used technique, and the
real proof of behaviour is always in the real world.  For this reason, we
also argue that every benchmark based on a minimal simulation should also
have an easy-to-construct physical analog.  However, this physical version
is not to be used as the primary benchmark.  Rather, this is meant as a
double-check that the system does actually behave as expected.

@@

The simplest controller for such a situation is a P (proportional) controller,
where $u=K_p(q_d - q)$.  This is often supplemented with a D (derivative) term,
which helps to slow the system down as it approaches the desired position,
thus avoiding overshooting and oscillation ($u=K_p(q_d - q) + K_d(\dot{q_d} - \dot{q})$),
leading to the standard PD controller.  Both $K_p$ and $K_d$ are constants that can be
tuned to particular situations.

@@

The standard solution to this problem is to add an I (integral) term ($K_i \int{(q_d-q) dt}$)
to the controller, making it a PID controller.  The idea here is that as the difference between where it is and
where we want it to be accumulates over time, the $K_i$ term gradually increases
how much extra force is being applied until it is large enough to counteract
the external force of gravity (or whatever other external forces are present).
However, this approach has great difficulty when $q_d$ changes, since the
external force due to gravity changes depending on the position of the arm $q$.
The controller ends up having to use the accumulated integral to ``relearn'' the
correct amount of extra force needed every time $q_d$ changes.

@@

Fortunately, there is an adaptive solution to this problem, and it is one that
fits well with neuromorphic hardware.  \cite{Slotine1987} shows that if you
express the influence of these other external forces as $\tau=Y(q) \omega$
(where $Y(q)$ is a fixed set of functions of $q$, such as $sin(q)$, and $\omega$
is a vector of scalar weights, one for each function in $Y$), then you can learn
to compensate for these external forces by using the learning rule $\Delta \omega = \alpha Y(q) u$,
where $u$ is the basic PD control signal.

Importantly, as pointed out by \cite{SannerSlotine1992} and \cite{Lewis1996}, rather than making explicit
assumptions about the exact functions that should be in $Y(q)$, we can use
a neural network approach where each neuron is a different function of $q$.  
As long as there is enough hetereogenetity (i.e. as long as the neural activity
forms a basis space that spans the desired space of functions), then the
learning rule will continue to work.  This approach has been used in the
Recurrent Error-driven Adaptive Control Hierarchy model of human motor control
(\citealt{dewolf2014}), and for quadcopter control [TODO: any citations for this?].
